Robust Estimation, Prediction and Control with \\ Linear Dynamics and Arbitrary Costs

### 2020-01-17 main.tex
Updates from Overleaf

Our contributions are the following:
In Section 2, we structured dynamics. In order to derive the confidence regions, we rely on the work of \citet{Abbasi2011} that provide confidence ellipsoid for the regularised least-square estimator. However, we need to extend their result by one dimension, with matricial features and vectorial noise where the original setting involved vectorial features and scalar noise.

@@

\begin{assumption}[Bounded noise]
\label{assumpt:bounded-noise}
The noise $\eta(t)$ is bounded
\[
\|\eta\|_\infty < \infty
\]
\end{assumption}

@@

From now on, we consider that we reached time $N$, which is now fixed, and that a confidence region $\cC_{[N],\delta}$ was obtained with data $\cD$ collected so far. The following sections tackle the optimisation of the robust control objective:
\begin{equation}
\label{eq:robust-control}
\max_\bu \underbrace{\min_{\substack{A(\theta) \in \cP \\ \bw\in[\underline{\omega},\overline{\omega}]^\Natural}} \left[\sum_{t=0}^\infty \gamma^t r(x(t,\bu,\bw))\right]}_{V^r(\bu)}
\end{equation}
where $\bu = (u_{N+1},u_{N+2},\cdots)$ and $\bw = (\omega_N, \omega_{N+1},\cdots)$ are the sequences of future controls and perturbations, respectively.

@@

@@

Since all our approximations were conservative, if we manage to find a control sequence such that no \textit{bad event} (e.g. a collision) happens with our surrogate objective, then we are guaranteed so they will not happen either when the controls are executed on the true system.

@@

In the case of bounded noise, model adequacy is simply measured by the violation of

One of the major benefits of using the family of linear models, compared to richer model classes, is that it enables to measure the adequacy of the modelling assumptions to the observations.

Following \citep{maillard:hal-01349727}, we define the model adequacy for an observation $x(t), u(t), \dot{x}(t)$ of the modelling assumptions $(A, \phi)$ trained on history $\cD_{[N]}$ by:
\begin{equation*}
    \alpha(x(t), u(t), \dot{x}(t)) = \sup_\delta \argmin_{\delta\in(0,1)} d\left(\dot{x}(t), \cC_{[N],\delta}(x(t), u(t))\right)
\end{equation*}
where $d(\dot x,\cC(x,u)) = \inf_{\hat{A}\in\cC} \left\|\hat{A}x + Bu - \dot{x}\right\|^2 + \|\eta\|_\infty^2$.
An adequacy of $0$ indicates a strong match of the assumptions, while an adequacy of $1$ indicates a strong mismatch. The

>>>>

Our contributions are the following:
In Section 2, structured dynamics. We extend the work of \citet{Abbasi2011} that provide a confidence ellipsoid for the regularised least-square estimator in the case of scalar noise and vector features to our setting of vector noise and matrix features.

@@

\begin{assumption}[Bounded noise]
\label{assumpt:bounded-noise}
The noise $\eta(t)$ is bounded
\[
\|\eta\|_\infty < \infty.
\]
In particular, we denote the coefficient-wise bounds over perturbations as $\underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)$.
\end{assumption}

@@

\paragraph{Robust objective}

From now on, we consider that we have reached step $N$, and that a confidence region $\cC_{[N],\delta}$ was obtained with data $\cD_{[N]}$ collected so far. The following sections tackle the optimisation of the robust control objective:
\begin{equation}
\label{eq:robust-control}
\max_\bu \underbrace{\min_{\substack{A(\theta) \in \cC_{[N],\delta} \\ \bw\in[\underline{\bw},\overline{\bw}]^\Natural}} \left[\sum_{n=1}^\infty \gamma^n R(x_n(\bu,\bw))\right]}_{V^r(\bu)}
\end{equation}
where $\bu = (u_{N+1},u_{N+2},\cdots)$ and $\bw = (\omega_N, \omega_{N+1},\cdots)$ are the sequences of future controls and perturbations, respectively. Here, we considered the bounded noise setting of \autoref{assumpt:bounded-noise}. In the sub-Gaussian noise setting of \autoref{assumpt:gaussian-noise}, we can use the same formulation by deriving high-confidence bounds $\underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)$ that each hold with probability $\delta_t$. By choosing $\delta_t = \frac{\delta}{t(t+1)}$, we have that the event $\{\forall t, \underline{\omega}(t) \leq \omega(t) \leq \overline{\omega}(t)\}$ holds with probability $1-\delta$.

@@

Limitations: set-based method assumes time-varying uncertainty where we have time-invariant uncertainty: $A(\theta)$ is fixed vs $A(\theta)$ can vary in $\cC_\delta$ at each step. Consequence: conservative overset.

@@

The consequence of \autoref{prop:lower-bound} is that since all our approximations were conservative, if we manage to find a control sequence such that no \textit{``bad event''} (e.g. a collision) happens with our surrogate objective, then we are guaranteed so they will not happen either when the controls are executed on the true system.

@@

One of the major benefits of using the family of linear models, compared to richer model classes, is that they provide strict conditions allowing to quantify the adequacy of the modelling assumptions to the observations.

TODO: from $\cC$ to confidence regions for $y_{n+1}$.

% Following \citep{maillard:hal-01349727}, we define the model adequacy for an observation $x(t), u(t), \dot{x}(t)$ of the modelling assumptions $(A, \phi)$ trained on history $\cD_{[N]}$ by:
% \begin{equation*}
%     \alpha(x(t), u(t), \dot{x}(t)) = \sup_\delta \argmin_{\delta\in(0,1)} d\left(\dot{x}(t), \cC_{[N],\delta}(x(t), u(t))\right)
% \end{equation*}
% where $d(\dot x,\cC(x,u)) = \inf_{\hat{A}\in\cC} \left\|\hat{A}x + Bu - \dot{x}\right\|^2 + \|\eta\|_\infty^2$.
% An adequacy of $0$ indicates a strong match of the assumptions, while an adequacy of $1$ indicates a strong mismatch. The
